---
title: "Bootstrap"
author: "Alison Elgass"
date: "11/14/2019"
output: html_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

## Start with data
Let’s create some simulated data.  
First generate x and an error sampled from a normal distribution, 
then a response y; this all gets stored in sim_df_const.  
  
Then I’ll modify this by multiplying the errors by a term that involves x, and create a new response variable y.
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
    error = error * .75 * x,
    y = 2 + 3 * x + error
)
```

What if we run a linear regression on each dataset (n = 250)
```{r}
lm(y ~ x, data = sim_df_const) %>%    #dataset 1
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(y ~ x, data = sim_df_nonconst) %>% #dataset 2
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


# Bootstrapping
Now write a function to take bootstrap samples  
_REMEMBER_* a bootstrap sample is the same n, **with** replacement  
so we will get a different sample, will likely have repeats
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

Try it with our dataset we made, then plot
```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

Now do it many times and store in **list columns**   
(so we take a bootstrap sample of n = 250, 1000 times)
```{r}
boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

### Do some kind of analysis....
```{r}
#for each strap_sample df, run a linear regression
bootstrap_results = boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, -models) %>% #we only care about 'results'
  unnest(results)
```
So we end up with 1,000 models (2,000 columns: beta0 and beta1), each
generated from a single bootstrap sample of n = 250


### Summarize the results
```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate)) #sd of our 1,000 b0's and b1's
```

Compare this to origingal model from nonconst data (just 1 sample)
```{r}
lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


# Bootstrap with modelr package
```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)
```
Wow so nice and easy!!!!!!!!!!!!

```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

