---
title: "Cross Validation"
author: "Alison Elgass"
date: "11/13/2019"
output: github_document
---

```{r }
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)
```

# Cross Validation "by hand"
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

Split into **training/testing,** using anti-join
```{r}
train_df = sample_n(nonlin_df, 80)                   #BLACK
test_df = anti_join(nonlin_df, train_df, by = "id")  #RED

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

### 3 different models
Now let's fit 3 models, using training data (none are nested)  
Jeff likes `mgcv::gam` for non-linear additive models
```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)

#plot smooth model
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

#plot wiggly model
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

or use `modelr::gather_predictions` to join/plot multiple
```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

We can see smooth model is best  
but let's also calculate the root mean square error
```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```


# Cross Validation using modelr
`corssv_mc` splits into training/testing multiple times, 
then stores in df using listcols
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

If we want to use gam, we have to coerce into a df
```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Now for **each** of these train/test sets, we need to (map to) 
1. fit the models  
2. calculate RMSE 
```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), 
                                       sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, 
                                ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, 
                                ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, 
                                ~rmse(model = .x, data = .y)))
```

Now plot to compare RMSE's
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

# An example


