---
title: "Linear Models Intro"
author: "Alison Elgass"
date: "11/7/2019"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

Ah yes our good friend air bnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)

```

## Fit our first linear model!
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
#automatically picks

summary(fit)
summary(fit)$coef
coef(fit)
```
Note that  
1. R automatically picks Bronx as reference category
2. Stars estimate = 32, i.e. $32 price hike for every 1 star increase  
  
Now just tidy the results a bit
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 2)

fit %>% 
  broom::glance() #also an option
```

### Take a look at factors, change ref category
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro), #order by frequency
    room_type = fct_infreq(room_type))

str(nyc_airbnb)

#Re-fit the linear model
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 2)
```

Now our reference category is Manhattan (the most frequent), 
so our model has changed!

## Diagnostics
```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() +
  ylim(-500, 500)

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  ylim(-500, 500)
```

# Hypothesis Testing
```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

## Nesting Data
How can we run a regression to predict price by stars & room type,
but differentiate by borough?  
First how to do this with interaction terms (not great)
```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Look at just Brooklyn
```{r}
nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

If we nest the dataset, so we have a separate dataset for each borough
then we can do a separate regression in each 
Let's try using nest and map
```{r}
nest_lm_res =
  nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)

nest_lm_res %>% 
  select(boro, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  pivot_wider(
    names_from = term, values_from = estimate) %>% 
  knitr::kable(digits = 3)
```

### Another example
```{r}
manhattan_airbnb = #only manhattan data
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  nest(data = -neighborhood) %>% #nest by neighborhood
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)

manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

